ms2

### 2017-08-10 ms2/ms2.Rmd
moved to summarize simply

```{r fnz_mean}
all_ineq %>%
  mutate_at(vars(matches('fnz')), function(x) x*100) %>%
  ggplot(aes(x=mean_cpb, xmin=mean_cpb-sem_cpb, xmax=mean_cpb+sem_cpb,
             y=mean_fnz, ymin=mean_fnz-sem_fnz, ymax=mean_fnz+sem_fnz,
             color=region, label=state_abbreviation)) +
  geom_point() +
  geom_linerange() +
  geom_errorbarh(height=0) +
  geom_text(nudge_x=0.04) +
  xlab('mean claims per beneficiary') +
  ylab('mean % beneficiaries with at least one claim') +
  theme_minimal()
```

>>>>

```{r fnz_mean_old}
all_ineq %>%
  mutate_at(vars(matches('fnz')), function(x) x*100) %>%
  ggplot(aes(x=mean_cpb, xmin=mean_cpb-sem_cpb, xmax=mean_cpb+sem_cpb,
             y=mean_fnz, ymin=mean_fnz-sem_fnz, ymax=mean_fnz+sem_fnz,
             color=region, label=state_abbreviation)) +
  geom_point() +
  geom_linerange() +
  geom_errorbarh(height=0) +
  geom_text(nudge_x=0.04) +
  xlab('mean claims per beneficiary') +
  ylab('mean % beneficiaries with at least one claim') +
  theme_minimal()
```
